\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Andrei Rykov} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+79255792590 \\ St. Petersburg, Russia} 
\address{\href{mailto:contact@faangpath.com}{andreyrykovspb@gmail.com} \\ \href{https://linkedin.com/in/agrykov}{LinkedIn} \\ \href{https://github.com/glendawur}{GitHub}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Data Science \& AI graduate with research experience, seeking full-time Ph.D. studies, ML Engineer and Data Scientist roles. My research interest are cluster analysis, representation learning and deep learning in general.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Master of Science} in Data Science and AI, Eindhoven University of Technology (TU/e) \hfill {2021-2023}\\
Graduation Thesis: Robust Deep Spectral Clustering \\
(Supervisor: dr. Sibylle Hess, Grade: 8/10)

{\bf Bachelor} in Business Informatics, Higher School Of Economics, Moscow \hfill {2017 - 2021}\\
Graduation Thesis: Application of Anomalous Clustering Methods for Determination of the Number of Clusters\\
(Supervisor: prof. Boris Mirkin, Grade: 9/10)
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Data Analysis & NumPy, SciPy, Pandas\\
Data Visualization & Matplotlib, Seaborn, Plotly, Dash\\
Machine Learning and Data Mining & Sci-Kit Learn\\
Deep Learning & PyTorch, TensorFlow\\
Data Management & PySpark, SQL (Transact-SQL), Neo4j, MongoDB\\
Programming Languages & Python, R, C\#, JavaScript \\
Techniques & Cluster Analysis, Predictive Analytics, Data Modeling\\
Languages & English (Advanced), German (Beginner), Russian (Native)\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Intern} \hfill Jul 2020\\
LIIS Engineering Systems \hfill \textit{St Petersburg, RU}
 \begin{itemize}
    \itemsep -3pt {} 
     \item  Prepared comparative survey about various mobile applications for charging e-cars.
     \item Developed technical documentation with preliminary recommendations for new platform. 
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{MirCl} {Small python package was developed on top of the code for the bachelor thesis and further research related with clustering and optimal choice of number of clusters. Package is planned to be edited to make a process of clustering easier and more informative. [\href{https://github.com/glendawur/MirCl}{GitHub}]}
\item \textbf{LinioSpace} {Participated in the development of public transport navigation system. As part of the project, JavaScript and Pug code for the UI of the website were written, adding a number of additional panels for the interactive map. In addition, several SQL procedures for the data processing and migration of graph information from RDBMS to graph database Neo4j were developed.}
\item \textbf{Business and IT: Development of Mobile App} {Business \& IT, Spring 2019. Combined student team of students from Higher School Of Economics and Rotterdam University of Applied Sciences. Android App for dutch-based company was developed using Kotlin.}
\end{rSection} 

%----------------------------------------------------------------------------------------
% \begin{rSection}{Extra-Curricular Activities} 
% \begin{itemize}
%     \item 	Organized Live-music parties "Party Out Loud" during the the period from 2018 to 2019 with more than 250 attendants.  
%     \item	Ex-author of music blog "HSR" [\href{https://vk.com/highschoolradio}{VK}].
% \end{itemize}


% \end{rSection}

% %----------------------------------------------------------------------------------------
% \begin{rSection}{Leadership} 
% \begin{itemize}
%     \item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
% \end{itemize}
% \end{rSection}


\end{document}
